Recurrent Neural Networks for object detection

### 2019-07-20 Paper/Paper_First_Draft.tex
adding more details for each of the paper, adding more citations and structuring the paragraphs

%<<<<<<< HEAD
\author{\IEEEauthorblockN{Bin Qassim Ahmad}
\IEEEauthorblockA{\textit{Technical University of Munich} \\
\textit{Department of Informatics}\\
Munich, Germany \\
ahmad.qasim@tum.de }
\and
\IEEEauthorblockN{Pettirsch Arnd}
\IEEEauthorblockA{\textit{Technical University of Munich} \\
\textit{Department of Informatics}\\
Munich, Germany \\
a.pettirsch@outlook.de}
}

@@

\subsection{Definition}
First, we want to introduce feature-based Video Object Detection methods. As defined, for example, in [1-2] feature-based Video Object Detection methods fuse detectors which integrate features from multiple frames into their video detection. In most of our papers those detectors use recurrent units to integrate the visual features from different frames.

@@

\subsection{Feature Selective Small Object Detection via Knowledge-based recurrent attentive neural networks}
\begin{figure}[h]
\includegraphics[width=\columnwidth]{KB-RANN-architecture}
\caption{Architecture Feature Selective Small Object Detection via Knowledge-based recurrent attentive neural networks}
\end{figure}
The aim of this paper is develop a real-time object detector for the purpose of autonomous driving. The network developed in this paper is termed as Knowledge-Based Recurrent Attentive Neural Network (KB-RANN) and the authors successfully compressed and accelerated their proposed model and deployed it to their own self-developed autonomous car. \newline
The authors use SqueezeNet for feature extractor because SqueezeNet can provide AlexNet level of accuracy but with 50 times less parameters. Although there are better performing models like VGGNet and ResNet, but these models are computationally expensive. They make a few changes in the SqueezeNet architecture, which include changing the kernel size and also fine-tuning the backend by adding two fire modules at the end. \newline
Attention mechanism is used to find the saliency maps from the deep feature maps obtained from SqueezeNet. Attention module obtains the input tensor X and outputs the saliency map $\tilde{X\textsubscript{t}}$. \newline
LSTM is used as a memory mechanism in order to find long term dependencies between different frames and the characteristics of Attention and LSTM are exploited together by fusing them with each other, this fused module is termed as RANN. As saliency feature extraction is applied on the original deep feature maps, it is possible that some of the information is lost. Multiple RANNs are cascaded together into a chain to minimize the effect of feature information loss. Moreover, the output H\textsubscript{t} of each LSTM is concatenated with the original feature map and used as an input for the next attention module to refine the saliency feature extraction process. \newline
The authors also add a domain and intuitive knowledge module to the KB-RANN architecture. It is assumed that traffic signs detection is one of the most important aspect of autonomous driving. The major focus of attention of a driver is at the center of vision and the traffic lights are always located at a bias from that central region of peoples' gazes. With these assumptions in place, domain knowledge about traffic signals is learned from the data itself by constraining the distribution to a 2D Gaussian function and learning the mean and covariance matrices from the data. \newline

\subsection{Looking fast and slow: memory-guided mobile video object detection}
\begin{figure}[h]
\includegraphics[width=\columnwidth]{looking-fast-and-slow-architecture}
\caption{Architecture Looking fast and slow: memory-guided mobile video object detection}
\end{figure}
The main contribution of this paper is the introduction of multiple feature extractors. Using multiple feature extractors, an interleaving policy can be defined which defines which feature extractor to use given the current state of detection. Using a intelligent interleaving policy and feature extractors with varying computational costs along with different feature representation capabilities, this paper aims to find a balance between detection accuracy and performance. \newline
Let \textit{m} being the number of feature extractors. For the implementation of this paper, the authors constraint $\textit{m}=2$, a d let f\textsubscript{1} be the feature extractor which is computationally more expensive while f\textsubscript{2} be the feature extractor which is cheaper. Both feature extractors use MobileNetV2 architecture. f\textsubscript{1} uses a depth of 1.4 with $320*320$ input frames resolution while f\textsubscript{2} uses a depth of 0.35 with a lower $160*160$ input frames resolution. \newline
A modified LSTM is used as a memory mechanism to preserve long term dependencies. The modifications in the LSTM are responsible for making the memory mechanism faster and also better at preserving long term dependencies. For faster memory mechanism, the authors make three modifications. They introduce bottlenecking and add a skip connection between the bottleneck and the output. Lastly, the LSTM states are grouped together and convulations are applied on each group seperately and the resultant states are then concatenated together to obtain the final states. The grouped convulations provide a speed-up. In order to improve the preservation of long term dependencies by the LSTM, the LSTM states are only updated when f\textsubscript{1} is run and not the f\textsubscript{2}, as feature maps obtained from f\textsubscript{2} are not of a higher quality as of f\textsubscript{1} and this can result in loss of important state information in the LSTM. \newline
SSD-style detection is applied on refined feature maps obtained from the LSTM for classification and bounding boxes. \newline
The interleaving policy which defines the feature extractor that should be used next is based on reinforcement learning. The state space of the reinforcement learning policy network $\pi$ consists of the LSTM states, $c\textsubscript{t}$, $h\textsubscript{t}$, as well as the differences between the states at different timestamps i.e. $c\textsubscript{t}-c\textsubscript{t-1}$, $h\textsubscript{t}-h\textsubscript{t-1}$ and lastly the action history $\eta\textsubscript{t}$. The action space has length \textit{m} and the action \textit{a} means that the feature extractor f\textsubscript{\textit{a}} should be run. \newline
It is observed by the authors that, despite the employment of the interleaving policy the real-time detection is limited by the execution of the expensive f\textsubscript{1} feature extractor. They introduce an asynchronous framework for running the feature extractors f\textsubscript{1} and f\textsubscript{2} extractors in parallel. During testing, this asynchronous framework results in better results. \newline

\subsection{Detect to Track and track to detect}
\begin{figure}[h]
\includegraphics[width=\columnwidth]{D&T-architecture}
\caption{Architecture Detect to Track and track to detect}
\end{figure}
This paper is based on the R-FCN\cite{b19} model and extends it for multiple frame and tracking. \newline
The R-FCN\cite{b19} detection process consists of two stages, firstly a Region Proposal Network (RPN) is used to find the candidate region of interests (ROIs) and then a ROI pooling layer is used to perform classification of the regions into classes or the background. The input to the ROI pooling layer comes from a convulational layer put in place at the end of the ResNet feature extractor with output $x^t_{cls}$. The ROI layer outputs position sensitive feature maps and using a softmax layer these position senstive feature maps can be converted to class probablities for each ROI. On a second branch, R-FCN places a convulational layer at the end of the ResNet feature extractor which outputs $x^t_{reg}$ and this ouput is again used as an input to ROI pooling layer which generates the bounding boxes. \newline
For each pair of frames I\textsuperscript{t}, I\textsuperscript{t+$\tau$}, a bounding box regression layer is introduced that performs position senstive ROI pooling on the concatentation of bounding box regression features $x^t_{reg}$, $x^{t-1}_{reg}$, which are also stacked with correlation maps, to perform bounding box transformation regression between frames. The correlation maps between the two frames are obtained by finding correlation between the feature maps of the two frames. Finding correlation on all the features in the feature maps will result in an explosion of dimensionality so the correlation maps are only limited to the local neighbors. Like mentioned before, the correlation maps are stacked with the bounding box features maps. \newline

@@

\subsection{Definition}
\begin{figure}[h]
\includegraphics[width=\columnwidth]{box-level-basic}
\caption{Box-Level-based Video Object Detection}
\end{figure}
Bounding Boxes and Class probabilities are fed into the network and are refined temporally and/or spatially.

\subsection{Optimizing Video Object Detection via Scale-Time Lattice}
\begin{figure}[h]
\includegraphics[width=\columnwidth]{scale-time-lattice}
\caption{Architecture Optimizing Video Object Detection via Scale-Time Lattice}
\end{figure}
The primary contribution of this paper is the Scale-Time Lattice which allows coarse detection, both temporally and spatially and then use temporal propagation and spatial refinement to go from coarse to fine detection. The lattice is composed of structures which connect together to perform the temporal and spatial operations. These structures are called Propagation and Refinement Units (PRUs). \newline
PRUs work on the basis of two operators $F_\tau$ and $F_S$, and by carefully allocating resources to the two operators, a balance between the detection accuracy and the performance can be acheived. Assuming that two frames are sampled from a video at time $t$ and $t+2\tau$, both at scale $s$, the $F_\tau$ operator tries to model the movement of the bounding boxes from time $t$ to $t+\tau$ and from time $t+2\tau$ to $t+\tau$ irrespective of the scale offset between the scale $s$ and the ground truth frame scale $s+1$. The modeling of the bounding boxes offset from scale $s$ to $s+1$ is the task of the $F_S$ operator. The figure depicting the PRU gives more information on this. \newline

@@

\section*{Acknowledgment}
Todo

\section*{References}

Please number citations consecutively within brackets \cite{b1}. The 
sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''

Number footnotes separately in superscripts. Place the actual footnote at 
the bottom of the column in which it was cited. Do not put footnotes in the 
abstract or reference list. Use letters for table footnotes.

Unless there are six authors or more give all authors' names; do not use 
``et al.''. Papers that have not been published, even if they have been 
submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
Capitalize only the first word in a paper title, except for proper nouns and 
element symbols.

For papers published in translation journals, please give the English 
citation first, followed by the original foreign-language citation \cite{b6}.

@@

>>>>

%<<<<<<< HEAD
\author{\IEEEauthorblockN{Bin Qasim Ahmad}
\IEEEauthorblockA{\textit{Technical University of Munich} \\
\textit{Department of Informatics}\\
Munich, Germany \\
ahmad.qasim@tum.de }
\and
\IEEEauthorblockN{Pettirsch Arnd}
\IEEEauthorblockA{\textit{Technical University of Munich} \\
\textit{Department of Informatics}\\
Munich, Germany \\
a.pettirsch@outlook.de}
}

@@

First, we want to introduce feature-based Video Object Detection methods. As defined, for example, in [1-2] feature-based Video Object Detection methods fuse detectors which integrate features from multiple frames into their video detection. In most of our papers those detectors use recurrent units to integrate the visual features from different frames.

@@

\subsection{Feature Selective Small Object Detection via Knowledge-based recurrent attentive neural networks \cite{b6}}
\begin{figure}[h]
\includegraphics[width=\columnwidth]{KB-RANN-architecture}
\caption{Architecture Feature Selective Small Object Detection via Knowledge-based recurrent attentive neural networks}
\end{figure}

The aim of this paper is develop a video object detector for the purpose of autonomous driving. The network developed in this paper is termed as Knowledge-Based Recurrent Attentive Neural Network (KB-RANN). \newline
The main contributions of the authors are:
\begin{itemize}
  \item An attention mechanism that works like human cognition. The attention mechanism can detect the salient features, which are important for the object detection problem and propagate them forward. This attention mechanism is based on previous work by Ashish Vaswani et. al. \cite{b30}. 
  \item A domain and intuitive knowledge module which can use the knowledge about traffic signals to produce feature maps.
  \item A model which has good ability for transfering knowledge. The authors obtained good results by evaluating the KB-RANN model on BTSD dataset \cite{b29}, which was trained on KITTI dataset \cite{b21}.
\end{itemize}
The KB-RANN, model is tested on KITTI and MS COCO17 dataset \cite{b31}, achieving 0.813 mAP and 0.578 mAP on all classes on those datasets respectively. The model performs better then several popular objection detection algorithms like Faster R-CNN \cite{b15}, RetinaNet \cite{b32} and SqueezeDet \cite{b33}.
The authors successfully compressed and accelerated their proposed model and deployed it to their own self-developed autonomous car. \newline

The authors use SqueezeNet \cite{b34} for feature extractor because SqueezeNet can provide AlexNet level of accuracy but with 50 times less parameters. Although there are better performing models like VGGNet and ResNet, but these models are computationally expensive. They make a few changes in the SqueezeNet architecture, which include changing the kernel size and also fine-tuning the backend by adding two fire modules at the end. This modified SqueezeNet architecture is given the term, SqueezeNet+. \newline

Attention mechanism is used to find the saliency maps from the deep feature maps obtained from SqueezeNet. Attention module obtains the input tensor X and outputs the saliency map $\tilde{X\textsubscript{t}}$. \newline

LSTM \cite{b18} is used as a memory mechanism in order to find long term dependencies between different frames and the characteristics of Attention and LSTM are exploited together by fusing them with each other, this fused module is termed as RANN. As saliency feature extraction is applied on the original deep feature maps, it is possible that some of the information is lost. Multiple RANNs are cascaded together into a chain to minimize the effect of feature information loss. Moreover, the output H\textsubscript{t} of each LSTM is concatenated with the original feature map and used as an input for the next attention module to refine the saliency feature extraction process. \newline

Lasty, The authors also add a domain and intuitive knowledge module to the KB-RANN architecture. It is assumed that traffic signs detection is one of the most important aspect of autonomous driving. The major focus of attention of a driver is at the center of vision and the traffic lights are always located at a bias from that central region of peoples' gazes. With these assumptions in place, domain knowledge about traffic signals is learned from the data itself by constraining the distribution to a 2D Gaussian function and learning the mean and covariance matrices from the data. \newline

For training and evaluation of the model, the authors use the KB-RANN model and MS COCO17 dataset. They compare the results with other popular object detection models. On the KITTI dataset the KB-RANN achieves the mAP of 0.813, compared to the 0.763 of SqueezeDet, 0.702 of Faster R-CNN and 0.601 of RetinaNet. The frames-per-second (FPS) at which KB-RANN operates are higher then the compared models. In order to signify the accuracy gain from the attention mechanism and the knowledge module, authors also train and evaluate different architectures, namely KB-RCNN in which the attention mechanism is replaced with convulational layers and RANN, which does not have knowledge-based module. KB-RANN achieves better accuracy then KB-RCNN and RANN on KITTI and MS COCO17 dataset, although the FPS achieved by KB-RCNN due to its recurrent nature are higher. Lastly, a KB-RANN model with parameters trained on the KITTI dataset is also tested on BTSD dataset to demonstrate the knowledge transfer capabilities.

\subsection{Looking fast and slow: memory-guided mobile video object detection \cite{b7}}
\begin{figure}[h]
\includegraphics[width=\columnwidth]{looking-fast-and-slow-architecture}
\caption{Architecture Looking fast and slow: memory-guided mobile video object detection}
\end{figure}
The authors aim to, replicate the capability of a human visual system of obtaining the "gist" of a scene. Using this sparse information, and amalgamating it with the more thorough information, a human visual system can effectively detect objects in its field of vision. In light of this, the main contributions of this paper are:
\begin{itemize}
	\item The introduction of multiple feature extractors. Some of those feature extractors are very light-weight but can provide a "gist" of the frame, while others can provide more accurate representation of a frame but at the cost of performance.
	\item A memory module, which can fuse the outputs of those feature extractors.
	\item An adaptive interleaving policy which uses reinforcement learning to find to decide, which feature extractor should be executed.
	\item The capability of executing multiple feature extractors asynchronously. So that, the light-weight feature extractors don't have to wait for the more expensive feature extractors.
\end{itemize}
The model is evaluated on the ImageNet VID 2015 dataset \cite{b35}, with extra data from the ImageNet DET \cite{b35} and MS COCO17 datasets \cite{b31}. The model manages to achieve a mAP of 0.593 at 72.3 FPS on a Pixel3 mobile device. \newline

Let \textit{m} be the number of feature extractors. For the implementation of this paper, the authors constraint $\textit{m}=2$, a d let f\textsubscript{1} be the feature extractor which is computationally more expensive while f\textsubscript{2} be the feature extractor which is cheaper. Both feature extractors use MobileNetV2 architecture \cite{b36}. f\textsubscript{1} uses a depth of 1.4 with $320*320$ input frames resolution while f\textsubscript{2} uses a depth of 0.35 with a lower $160*160$ input frames resolution. \newline

A modified LSTM \cite{b18} is used as a memory mechanism to preserve long term dependencies. The modifications in the LSTM are responsible for making the memory mechanism faster and also better at preserving long term dependencies. For faster memory mechanism, the authors make three modifications. They introduce bottlenecking and add a skip connection between the bottleneck and the output. Lastly, the LSTM states are grouped together and convulations are applied on each group seperately and the resultant states are then concatenated together to obtain the final states. The grouped convulations provide a speed-up. In order to improve the preservation of long term dependencies by the LSTM, the LSTM states are only updated when f\textsubscript{1} is run and not the f\textsubscript{2}, as feature maps obtained from f\textsubscript{2} are not of a higher quality as of f\textsubscript{1} and this can result in loss of important state information in the LSTM. \newline
SSD-style \cite{b17} detection is applied on refined feature maps obtained from the LSTM for classification and bounding boxes. \newline

The interleaving policy which defines the feature extractor that should be used next is based on reinforcement learning. The state space of the reinforcement learning policy network $\pi$ consists of the LSTM states, $c\textsubscript{t}$, $h\textsubscript{t}$, as well as the differences between the states at different timestamps i.e. $c\textsubscript{t}-c\textsubscript{t-1}$, $h\textsubscript{t}-h\textsubscript{t-1}$ and lastly the action history $\eta\textsubscript{t}$. The action space has length \textit{m} and the action \textit{a} means that the feature extractor f\textsubscript{\textit{a}} should be run. \newline

It is observed by the authors that, despite the employment of the interleaving policy the real-time detection is limited by the execution of the expensive f\textsubscript{1} feature extractor. They introduce an asynchronous framework for running the feature extractors f\textsubscript{1} and f\textsubscript{2} extractors in parallel. During testing, this asynchronous framework provides better results. \newline

As mentioned before, the authors use ImageNet VID 2015 dataset for training and evaluation, which has 30 classes in total, along with the addition of extra data from ImageNet DET and MS COCO17, but this extra data is limited to the classes contained within ImageNet VID. All results are reported, using a Pixel 3 mobile device. The results are compared with, baseline single-frame detection model i.e. MobilenetV2-SSDLite (mAP: 0.420, FPS: 14.4), LSTM-based model i.e. MobilenetV2-SSDLite+LSTM (mAP: 0.451, FPS: 14.6) and the state of the art mobile video object detection model of Zhu et. al. (mAP: 0.602, FPS: 25.6). The proposed model by authors manages to achieve a mAP of 0.593 at 72.3 FPS. The authors also perform evaluation using slight variations of the proposed architecture i.e. Non-interleaved, Interleaved only, Interleaved+Async and Interleaved+Adaptive+Async, in order to test the significance of different components of the architecture on the end results. The Interleaved+Adaptive+Async provides the most balanced end result. \cite{b37}. Although the

\subsection{Detect to Track and track to detect}
\begin{figure}[h]
\includegraphics[width=\columnwidth]{D&T-architecture}
\caption{Architecture Detect to Track and track to detect}
\end{figure}
In this paper, the authors aim to perform, detection and tracking simultaneously using a fully convulational network by infering a "tracklet" over multiple frames.  This paper is based on the R-FCN\cite{b19} model and extends it for multiple frame and tracking. The main contributions of this paper are:
\begin{itemize}
	\item Finding correlation maps of two feature maps of adjacent frames. These correlation maps are used to estimate the local displacement between frames.
	\item Using ROI-tracking layer to regress bounding boxes over multiple frames.
	\item Linking the detections based on tracklets to infer long-term tubes of objects over the course of the video.
\end{itemize}
The proposed model is trained and evaluated on the ImageNet VID dataset \cite{b35}, consisting of 30 classes. The model achieves an overall mAP of 0.82. \newline

The R-FCN\cite{b19} detection process consists of two stages, firstly a Region Proposal Network (RPN)\cite{b38} is used to find the candidate region of interests (ROIs) and then a ROI pooling layer\cite{b39} is used to perform classification of the regions into classes or the background. The input to the ROI pooling layer comes from a convulational layer put in place at the end of the ResNet-101 feature extractor\cite{b40} with output $x^t_{cls}$. The ROI layer outputs position sensitive feature maps and using a softmax layer these position senstive feature maps can be converted to class probablities for each ROI. On a second branch, R-FCN places a convulational layer at the end of the ResNet-101 feature extractor which outputs $x^t_{reg}$ and this ouput is again used as an input to ROI pooling layer which generates the bounding boxes. \newline

For each pair of adjacent frames I\textsuperscript{t}, I\textsuperscript{t+$\tau$}, a bounding box regression layer is introduced that performs position senstive ROI pooling on the concatentation of bounding box regression features $x^t_{reg}$, $x^{t-1}_{reg}$, which are also stacked with correlation maps, to perform bounding box transformation regression between frames. The correlation maps between the two frames are obtained by finding correlation between the feature maps of the two frames. Finding correlation on all the features in the feature maps will result in an explosion of dimensionality so the correlation maps are only limited to the local neighbors. Like mentioned before, the correlation maps are stacked with the bounding box features maps. \newline

In practical uses, using all frames of the video is not the most efficient way of detection and tracking, as a lot of information between adjacent frames is redundant and also due to GPU memory and computational restrictions, only a certain number of frames can be processed in the GPU at the same time. Due to this, the authors employ a technique similar to action localization\cite{b41} to obtain an optimal path through a video. \newline

As mentioned above, the proposed model is trained and evaluated on the ImageNet VID dataset. A comparison is made with the R-FCN detector (mAP: 0.742), which the proposed model is based on, the ILSVRC 2015\cite{b42} (mAP: 0.738) winner and the ILSVRC 2016\cite{b43} (mAP: 0.762) winner. DT performs the best with a mAP of 0.82. A comparison between slight variations of the DT model are also evaluated. Firstly, using different feature extractor backbones: ResNet-50 (mAP: 0.767), ResNet-101 (mAP: 0.80) and Inception-v4 (mAP: 0.821)\cite{b44} and secondly using the ResNet-101 backbone but a temporal sampling rate $\tau$ of 10 (mAP: 0.786).

@@

\begin{figure}[h]
\includegraphics[width=\columnwidth]{box-level-basic}
\caption{Box-Level-based Video Object Detection}
\end{figure}
Bounding Boxes and Class probabilities are fed into the network and are refined temporally and/or spatially.

\subsection{Optimizing Video Object Detection via Scale-Time Lattice}
\begin{figure}[h]
\includegraphics[width=\columnwidth]{scale-time-lattice}
\caption{Architecture Optimizing Video Object Detection via Scale-Time Lattice}
\end{figure}
The aim of this paper, is to propose an architecture which is balanced and flexible enough to allow prioritisation of accuracy or performance with minimal effort. The primary contributions of this paper are:
\begin{itemize}
	\item The Scale-Time Lattice, which provides a rich design space.
	\item A detection framework which provides good accuracy to performance trade-off.
	\item A novel key-frame extraction policy, which is based on the ease of detection.
\end{itemize}

The Scale-Time Lattice allows coarse detection, both temporally and spatially and then use temporal propagation and spatial refinement to go from coarse to fine detection. \newline

The Scale-time lattice is composed of structures which connect together to perform the temporal and spatial operations. These structures are called Propagation and Refinement Units (PRUs). PRUs work on the basis of two operators $F_\tau$ and $F_S$, and by carefully allocating resources to the two operators, a balance between the detection accuracy and the performance can be acheived. Assuming that two frames are sampled from a video at time $t$ and $t+2\tau$, both at scale $s$, the $F_\tau$ operator tries to model the movement of the bounding boxes from time $t$ to $t+\tau$ and from time $t+2\tau$ to $t+\tau$ irrespective of the scale offset between the scale $s$ and the ground truth frame scale $s+1$. The modeling of the bounding boxes offset from scale $s$ to $s+1$ is the task of the $F_S$ operator. The figure depicting the PRU gives more information on this. \newline

The most straight-forward keyframe extraction policy is a uniform i.e. to use keyframes from the video after uniform intervals but an intelligent keyframe extraction policy can be used to increase the accuracy of the results. To that effect, the authors introduce a ease of detection cofficient e. If during detection, the value of e falls beneath a certain threshold that the sample rate of the frames from the video is increased. This can happen if there are a lot of objects on the screen or the objects are moving too quickly. \newline

The proposed model has an mAP of 0.79 at 60 FPS on the ImageNet VID dataset. \newline

@@

\newpage

@@

\bibitem{b29} Radu Timofte, Karel Zimmermann, Luc Van Gool. Multi-view traffic sign detection, recognition, and 3D localisation. 2009.
\bibitem{b30} Ashish Vaswani, Noam Shazeer, Niki Parmar, Jakob Uszkoreit. Attention Is All You Need. 2017.
\bibitem{b31} Tsung-Yi Lin, Michael Maire, Serge Belongi, Lubomir Bourde, Ross Girshick et. al. Microsoft COCO: Common Objects in Context. 2015.
\bibitem{b32} T.-Y. Lin, P. Goyal, R. Girshick, K. He, P. Dollar, Focal loss ´
for dense object detection. 2017.
\bibitem{b33} B. Wu, F. Iandola, P. H. Jin, K. Keutzer. Squeezedet: Unified, small, low power fully convolutional neural networks for real-time object detection for autonomous driving. 2016.
\bibitem{b34} Forrest N. Iandola, Song Han, Matthew W. Moskewicz, Khalid Ashraf, William J. Dally, Kurt Keutzer. Squeezenet: Alexnet-Level Accuracy With 50X Fewer Parameters And <0.5MB Model Size. 2016.
\bibitem{b35} O. Russakovsky, J. Deng, H. Su, J. Krause, S. Satheesh, S. Ma, Z. Huang, A. Karpathy, A. Khosla, M. Bernstein, et al. Imagenet large scale visual recognition challenge. 2015.
\bibitem{b36} M. Sandler, A. Howard, M. Zhu, A. Zhmoginov, L. Chen. Mobilenetv2: Inverted residuals and linear bottlenecks. 2018.
\bibitem{b37} X. Zhu, J. Dai, X. Zhu, Y. Wei, and L. Yuan. Towards high performance video object detection for mobiles. 2018.
\bibitem{b38} S. Ren, K. He, R. Girshick, and J. Sun. Faster R-CNN: Towards real-time object detection with region proposal networks. 2016.
\bibitem{b39} J. Dai, Y. Li, K. He, and J. Sun. R-FCN: Object detection via region-based fully convolutional networks. 2016.
\bibitem{b40} K. He, X. Zhang, S. Ren, and J. Sun. Deep residual learning for image recognition. 2016.
\bibitem{b41} S. Saha, G. Singh, M. Sapienza, P. H. Torr, and F. Cuzzolin. Deep learning for detecting multiple space-time action tubes in videos. 2016.
\bibitem{b42} K. Kang, H. Li, J. Yan, X. Zeng, B. Yang, T. Xiao, C. Zhang, Z. Wang, R. Wang, X. Wang, and W. Ouyang. T-CNN: tubelets with convolutional neural networks for object detection from videos. 2016.
\bibitem{b43} J. Yang, H. Shuai, Z. Yu, R. Fan, Q. Ma, Q. Liu, and J. Deng. ILSVRC2016 object detection from video: Team NUIST. 2016.
\bibitem{b44} Christian Szegedy, Sergey Ioffe, Vincent Vanhoucke. Inception-v4, Inception-ResNet and the Impact of Residual Connections on Learning. 2016.
